Data Prep: IUCN and AquaMaps

### 2016-02-16 data_explore/data_prep.Rmd
pushing new version of acquiring observation information

``` {r get_counts, echo = FALSE}
x <- occ_search(scientificName = spp_iucn_marine$sciname[1:100], fields = 'minimal', limit = 25)
y <- sapply(x, function(x) x$meta$count)
```

>>>>

``` {r counts_spp_all_observations}
spp_all <- read_csv(file.path(dir_data, 'spp_all.csv'))

library(rgbif)
# library(robis)

system.time({
  x <- occ_search(scientificName = spp_all$sciname[1:100], fields = 'minimal', limit = 1)
  ### seems linear - 10 names ~ 2.5 sec, 100 names ~ 25 sec, 1000 names, ~250 sec
  ### so 30000 names ~ 7500 sec or 2 hours
})
y <- sapply(x, function(x) x$meta$count)
gbif_occur <- data.frame(sciname = names(y), gbif_occ = y)

gbif_occur <- gbif_occur %>% 
  left_join(spp_all %>%
              select(iucn_sid, am_sid, sciname),
            by = 'sciname') %>%
  left_join(read_csv(file.path(dir_data_remote, 'aquamaps/v2015/csv/speciesoccursum.csv')) %>%
                       select(am_sid = speciesid, occurcells),
                     by = 'am_sid')

# plot(ln_obs ~ ln_occurcells, data = gbif_occur)
# plot(obs ~ occurcells, data = gbif_occur)
# print(summary(lm(obs ~ occurcells, data = gbif_occur)))

write_csv(gbif_occur, file.path(dir_data, 'gbif_occurrence_df.csv'))

source('obis_count.R')
scinames <- spp_all$sciname[1:100]

obis_occur <- obis_count(scinames)

obis_occur <- obis_occur %>% 
  left_join(spp_all %>%
              select(iucn_sid, am_sid, sciname),
            by = 'sciname') %>%
  left_join(read_csv(file.path(dir_data_remote, 'aquamaps/v2015/csv/speciesoccursum.csv')) %>%
                       select(am_sid = speciesid, occurcells),
                     by = 'am_sid')

write_csv(obis_occur, file.path(dir_data, 'obis_occurrence_df.csv'))

totes_occur <- obis_occur %>%
  left_join(gbif_occur)
